Do expert pianists adapt their pedagogical demonstrations to novices' skills?

### 2023-07-06 paper/manuscript.Rmd
correct title mistake for figure
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

ptof_all_plot <- ggplot(vel_diff[Subcomponent2 == "PtoF" & Category != "baseline"], aes(x = Dynamics, y = Mean, color = Articulation)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KV Difference (-127-127)", title = "KV Difference - PtoP") + scale_y_continuous(breaks = seq(-10, 40, 10), limits = c(-10, 40)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

>>>>

ptof_all_plot <- ggplot(vel_diff[Subcomponent2 == "PtoF" & Category != "baseline"], aes(x = Dynamics, y = Mean, color = Articulation)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KV Difference (-127-127)", title = "KV Difference - PtoF") + scale_y_continuous(breaks = seq(-10, 40, 10), limits = c(-10, 40)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")
